\subsection{Assume-Guarantee Reasoning}
\label{subsec:agree}
The Assume Guarantee Reasoning Environment (AGREE) is a tool for formal analysis of behaviors in AADL models~\cite{NFM2012:CoGaMiWhLaLu}.  It is implemented as an AADL annex and annotates AADL components with formal behavioral contracts. Each component's contracts can include assumptions about the component's inputs and guarantees about the component's outputs as well as predicates describing how the state of the component evolves over time.

AGREE contracts can be used to capture the functional requirements at each level of the hierarchy. Once the model has been reviewed and the requirements captured have been validated, the back-end analysis can be conducted to verify if each level of the model implements its higher level requirements correctly.

AGREE translates an AADL model and the behavioral contracts into Lustre~\cite{Halbwachs91:IEEE} and then queries a user-selected
model checker to conduct the back-end analysis. This analysis can be performed compositionally or monolithically. In monolithic analysis, the model is flattened and the top level property is proved using the leaf level component properties. Due to the state space explosion problem inherent in such large scale verification problems, this method does not scale well. On the other hand, compositional analysis begins with the lowest level components and seeks to prove the properties one level above. The analysis continues breaking the large problem into many smaller problems. This approach allows the analysis to scale to much larger systems~\cite{QFCS15:backes, NFM2012:CoGaMiWhLaLu}.

In prior work, an initial failure effect modeling capability was added to the AADL/AGREE language and tool set~\cite{Stewart17:IMBSA}. This work is an extension in hopes that this tool can be used to satisfy system safety objectives of ARP4754A and ARP4761.  




