Today's software development projects must respond to fierce competition, a
constantly  changing marketplace, and rapid technological innovation. Agile
development processes are popular when attempting to respond to these changes in
a controlled manner; however, selecting an ill-suited process may increase
project costs and risk.  Before adopting a seemingly promising agile approach,
we desire to evaluate the approach's applicability in the context of the
specific product, organization, and staff.  Simulation provides a means to do
this.  However, in order to simulate agile processes we require both the ability
to model individual behavior as well as the decoupling of the process and
product.  To our knowledge, no existing simulator nor underlying simulation
model provide a means to do this.

To address this gap, we propose a process simulation reference model
that provides the constructs and relationships for capturing the interactions among
the individuals, product, process, and project in a holistic fashion.  As a
means for evaluating this reference model, we plan to produce a simulation
framework on which to execute concrete representations of processes encoded 
using the reference model.

Our expected contributions are a reference model that can be used to encode
simulatable agile process models---models that incorporate the process as well
as the project environment---and an initial simulation framework that allows us
to execute models encoded using our reference model.  This work lays the
groundwork for detailed \apriori process evaluation and enables future research
into process development.
