\subsection{Background Information on Toolsuite}
The toolsuite used to perform these analyses are described in this section. The algorithms in this paper are implemented in the Safety Annex for the Architecture Analysis and Design Language (AADL) and require the Assume-Guarantee Reasoning Environment (AGREE)~\cite{NFM2012:CoGaMiWhLaLu} to annotate the AADL model in order to perform verification using the back-end model checker \jkind~\cite{2017arXiv171201222G}. 

\textbf{Architecture Analysis and Design Language}
We are using the Architectural Analysis and Design Language (AADL) to construct system architecture models. AADL is an SAE International standard that defines a language and provides a unifying framework for describing the system architecture for ``performance-critical, embedded, real-time systems''~\cite{AADL_Standard,FeilerModelBasedEngineering2012}. %An AADL model describes a system in terms of a hierarchy of components and their interconnections, where each component can either represent a logical entity (e.g., application software functions, data) or a physical entity (e.g., buses, processors). 
Language annexes to AADL provide a richer set of modeling elements for various system design and analysis needs.% (e.g., performance-related characteristics, configuration settings, dynamic behaviors). 
The language definition is sufficiently rigorous to support formal analysis tools that allow for early phase error/fault detection. 

\textbf{Compositional Analysis} 
Complex systems are usually composed from libraries of components. The specification of these systems are decomposed into properties of each individual component~\cite{clarke1989compositional}. %Compositional verification is then employed to ensure the correctness of the top level safety properties based on the support of lower level component contracts. 
Compositional verification partitions the formal analysis of a system architecture into verification tasks that correspond into the decomposition of the architecture. A component contract is an assume-guarantee pair. Intuitively, the meaning of a pair is: if the assumption is true, then the component will ensure that the guarantee is true. %The components of a system are organized hierarchically and each layer of the architecture is viewed a system. 
For any given layer, the proof consists of demonstrating that the system guarantee is provable given the guarantees of its direct subcomponents and the system assumptions~\cite{cofer2012compositional}. %This proof is performed one layer at a time starting from the top level of the system. 
When compared to monolithic analysis (i.e., analysis of the flattened model composed of all components), the compositional approach allows the analysis to scale to much larger systems~\cite{NFM2012:CoGaMiWhLaLu,heckel1998compositional,cofer2012compositional}.

\textbf{Assume Guarantee Reasoning Environment}
The Assume Guarantee Reasoning Environment (AGREE) is a tool for formal analysis of behaviors in AADL models and supports compositional verification~\cite{NFM2012:CoGaMiWhLaLu}.  It is implemented as an AADL annex and is used to annotate AADL components with formal behavioral contracts. Each component's contracts can include assumptions and guarantees about the component's inputs and outputs respectively. A guarantee defines the nominal behavior of components and an assumption defines what the component expects from its environment. AGREE translates an AADL model and the behavioral contracts into Lustre~\cite{Halbwachs91:IEEE} and then queries the \jkind model checker to conduct the back-end analysis~\cite{2017arXiv171201222G}. 

\textbf{JKind}
JKind is an open-source industrial infinite-state
inductive model checker for safety properties~\cite{2017arXiv171201222G}. Models and properties in JKind are specified in Lustre~\cite{Halbwachs91:IEEE}, a synchronous dataflow language, using the theories of linear real and integer arithmetic. JKind uses SMT-solvers to prove and falsify multiple properties in parallel.

\textbf{Safety Annex for AADL}
The Safety Annex for AADL provides the ability to reason about faults and faulty component behaviors in AADL models~\cite{Stewart17:IMBSA,stewart2020safety}. In the Safety Annex approach, AGREE is used to define the nominal behavior of system components; faults are then woven into the nominal model and JKind is used to analyze the behavior of the system in the presence of faults. Faults describe deviations from the nominal behavior and are attached to the outputs of components in the system.%The Safety Annex supports behavioral specification of faults and their implicit propagation through behavioral relationships in the model as well as explicit propagation through dependencies. 